Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-06-07 code/rmarkdown/article.Rmd
+ fixes to debugging parameters + added refs to article

The first outlier detection method we used involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456]. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. Following their methodology, we first grouped conspecifics into genetic lineages to avoid falsely classifying loci as adaptive. To complete this first step, for each species, we fit the admixture and correlated alleles model implemented in \texttt{Structure} [version 2.3.4; XXXX] assuming various numbers of populations (K = `r min(structure.params.LST[[MODE]]$maxpops)`--`r max(structure.params.LST[[MODE]]$maxpops)`; `structure.params.LST[[MODE]]$numruns` replicates per K; `r structure.params.LST[[MODE]]$admburnin` admixture burnin iterations; `r structure.params.LST[[MODE]]$burnin` burnin iterations; `r structure.params.LST[[MODE]]$numreps` iterations used for inference). We used the variant of Evanno's K method used in \texttt{Structure Harvester} [XXX] to identify the most suitable number of populations separately for each species. We used \texttt{ClumPP} [version 1.1.2; @r459] to combine replicate runs to group individuals into populations (greedy algorithm using the _G_ static; `r structure.params.LST[[MODE]]$repeats` iterations). After the \texttt{ClumPP} analysis, if most of the individuals for a given species (> 50 %) had uncertain population memberships (< 75 % probability for most likely population) then we treated this species as containing only a single population. We then ran $\texttt{Bayescan}$ for each species using these populations [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. Additionally, we omitted individuals from the \texttt{Bayescan} analysis if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

>>>>

The first outlier detection method we used involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456]. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. Following their methodology, we first grouped conspecifics into genetic lineages to avoid falsely classifying loci as adaptive. To complete this first step, for each species, we fit the admixture and correlated alleles model implemented in \texttt{Structure} [version 2.3.4; r@461; r@462] assuming various numbers of populations (K = `r min(structure.params.LST[[MODE]]$maxpops)`--`r max(structure.params.LST[[MODE]]$maxpops)`; `structure.params.LST[[MODE]]$numruns` replicates per K; `r structure.params.LST[[MODE]]$admburnin` admixture burnin iterations; `r structure.params.LST[[MODE]]$burnin` burnin iterations; `r structure.params.LST[[MODE]]$numreps` iterations used for inference). We applied the Evanno's K method variant used in \texttt{Structure Harvester} to identify the most suitable number of populations separately for each species [@r460; @r498]. We used \texttt{ClumPP} [version 1.1.2; @r459] to combine replicate runs to group individuals into populations (greedy algorithm using the _G_ static; `r clumpp.params.LST[[MODE]]$repeats` iterations). After the \texttt{ClumPP} analysis, if most of the individuals for a given species (> 50 %) had uncertain population memberships (< 75 % probability for most likely population) then we treated this species as containing only a single population. We then ran $\texttt{Bayescan}$ for each species using these populations [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. Additionally, we omitted individuals from the \texttt{Bayescan} analysis if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

### 2016-06-07 code/rmarkdown/supporting_information.Rmd
+ find best K using evanno's method
+ fixes to debugging parameters + added refs to article

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue. Note that \\textit{',gsub('\\_', '\\ ', missing.species),'} was omitted from analysis.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
) %>% mutate(presence=factor(c('absent', 'present')[presence+1]))

@@

		curr.probs <- spp.StructureAnalysis.LST[[i]]@results@summary %>%

@@

is.speciesPlottable <- function(i) {
	return(i <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[i] %in% missing.species) & !is.na(unique(spp.samples.DF$species)[i]))
}
```

>>>>

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
) %>% mutate(presence=factor(c('absent', 'present')[presence+1]))

@@

		curr.probs <- structurer:::sample.membership(spp.StructureCollection.LST[[i]]) %>%

@@

is.speciesPlottable <- function(i) {
	if (i <= general.params.LST[[MODE]]$n.spp)
		return(FALSE)
	return(!is.na(unique(spp.samples.DF$species)[i]))
}
```
